---
title: "preprocess_Exp3"
output: html_notebook
---

```{r}
# load packages
library(tidyverse)
library(ggplot2)
```


```{r}
df_raw <- list.files(file.path("./3_4_1_1_RawData"), pattern = "exp3_.*\\.csv$") %>%
  # 对读取到的所有.out文件x都执行函数read.table
  lapply(function(x) read.csv(file.path("./3_4_1_1_RawData", x), header = TRUE)) %>%
    # 读取被试人口学信息
  lapply(function(df) mutate(df,subj_idx = as.numeric(jsonlite::fromJSON(response[5])$Q0), 
          gender = jsonlite::fromJSON(response[6]),
          year = jsonlite::fromJSON(response[7])$Q0,
          education = jsonlite::fromJSON(response[8])$Q0,
          dist = view_dist_mm[9],
          rt = as.numeric(rt)))%>%
  bind_rows()

```


```{r}
df <- df_raw %>% 

  # 选择变量
  select(subj_idx, 
         gender, 
         year, 
         #education, 
         #dist, 
         rt, 
         correct_response, 
         correct, 
         key_press, 
         Image, 
         shape, # 无
         condition,
         trial_type) %>%
         # label # 无
  # 选择正式实验试次
  dplyr::filter(trial_type == "psychophysics" & 
                condition != "prac_self" & 
                condition !="prac_friend" & 
                condition !="prac_stranger") %>%
  mutate(
    ACC = 
      case_when(
        correct == "false" ~ 0, 
        correct == "true" ~ 1),

    )%>%
  # 剔除无关变量
  select(-correct_response,
         -correct,
         -key_press,
         -Image, 
         # -text,
         -trial_type,
         )
write.csv(df,file = "exp3_long.csv")
```


```{r}
#df <- df %>%
    #select(subj_idx,gender,year,rt,key_press,correct,text,condition,matchness,label,ACC) 
  
#write.csv(df,file = "exp2_long.csv")
```


```{r}
#正确率计算
  df_acc <- df %>%
  dplyr::mutate(ACC = ifelse(ACC == 1,1,0)) %>%
  dplyr::group_by(subj_idx,
                  condition,
                  shape
                  )%>%
  dplyr::summarise(
    N = length(ACC),
    countN = sum(ACC),
    ACC = sum(ACC) / length(ACC)
  ) 
  df_acc
```


```{r}
df_acc <- df_acc %>%
    select(subj_idx,condition,shape,ACC) %>%
   pivot_wider(names_from = c("shape", "condition"), values_from = "ACC")
  
write_excel_csv(df_acc,file = "exp3_acc_wide.csv")
```


```{r}
df_desc <- df %>%
          select(everything())%>%
          dplyr::filter(ACC == 1)%>%
          group_by(subj_idx,
                   condition,
                   shape)%>%
          summarize(n = n(),
                    rt = mean(rt, na.rm = TRUE))%>%
          ungroup()
df_desc
df_desc %>% 
  select(-n) %>% 
pivot_wider(names_from = c("shape", "condition"), values_from = "rt") %>% 
write_excel_csv("exp3_rt_wide.csv")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
